Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Specs are forests!
Rspec -> RSpec + better example

If we have evidence that does not fit into the user documentation, but
would rather be part of a design document, we use Hspec.  Hspec
provides an EDSL for defining specs.  A spec organizes evidence in a
tree structure, and it is defined with \texttt{it} and
\texttt{describe}.

@@

The problem of the original Hspec is that it does not provide
a mechanism to express \emph{expectation}\/s with
BDD terminology.
For instance,
it still uses HUnit
assertions, which are TDD
terminologies. In BDD, they are replaced with design terminologies.
The following Rspec example shows the ``should'' expectation keyword:

\begin{quote}
\small
\begin{verbatim}
23.should eq(23)
\end{verbatim}
\end{quote}

\noindent Another example is exceptions. Hspec does not yet provide a
mechanism to express expectation on exceptions. The following is
how to express expectation on an exception in Rspec:

>>>>

If we have evidence that does not fit into the user documentation, but
would rather be part of a design document, we use Hspec.  Hspec
provides an EDSL for defining specs.  A spec organizes evidence in a
tree structure (or a forest, to be accurate), and it is defined with \texttt{it} and
\texttt{describe}.

@@

The problem of the original Hspec is that it does not provide
a mechanism to express \emph{expectation}\/s with
BDD terminology.
For instance,
it still uses HUnit
assertions, which are TDD
terminologies. In BDD, they are replaced with design terminologies.
The following RSpec example shows the ``should'' expectation keyword:

\begin{quote}\small\begin{verbatim}
[1, 2, 3].reverse.should eq([3, 2, 1])
\end{verbatim}\end{quote}

\noindent Another example is exceptions. Hspec does not yet provide a
mechanism to express expectation on exceptions. The following is
how to express expectation on an exception in RSpec:
